Investigating Determinism of Game Engines for Autonomous Vehicle Verification

### 2020-05-26 paper/cav_determinisim_main.tex
added citation to definition of determinism

% Game engines for SBV
Compared to the vehicle dynamics simulators and traffic-level simulators used by manufacturers~\cite{FrameworkAndChallenges}, game engines offer a convenient simulation solution that meets many of the requirements for the development and functional safety testing of AVs in simulation. 
%
\todo[inline]{GC Replace: However, several challenges remain; one of these is determinism. with: However, game engines are designed principally for user experience whereas the requirements for CAV verification is not user experience but determinism.}
%
% What is a deterministic system
Deterministic, in this context, refers to the property of causality given a temporal development of events such that any state is completely determined by prior states.
%
Herein the term \textit{simulation variance} is used to refer to how simulation traces and outputs vary, when the same stimulus is provided repeatedly under identical initial conditions. Specifically, we focus on the variance of actor paths within a given scenario.

>>>>

% Game engines for SBV
Compared to the vehicle dynamics simulators and traffic-level simulators used by manufacturers~\cite{FrameworkAndChallenges}, game engines offer a convenient simulation solution that meets many of the requirements for the development and functional safety testing of AVs in simulation. 
%
\todo[inline]{GC Replace: However, several challenges remain; one of these is determinism. with: However, game engines are designed principally for user experience whereas the requirements for CAV verification is not user experience but determinism.}
%
% What is a deterministic system
Deterministic, in this context, refers to the property of causality given a temporal development of events such that any state is completely determined by prior states~\cite{Schumann2010}.
%
Herein the term \textit{simulation variance} is used to refer to how simulation traces and outputs vary, when the same stimulus is provided repeatedly under identical initial conditions. Specifically, we focus on the variance of actor paths within a given scenario.
